Dominance Regions for Imaginary $\bfg$-vectors

### 2020-06-09 dominance_regions.tex
Limit proof

  \section{Rank Two}
  Fix integers $b,c>0$ and assume $bc\ge4$.
  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2r}$ joined to $t_{2r+1}$ by an edge labelled $1$ and $t_{2r-1}$ joined to $t_{2r}$ by an edge labelled $2$.
  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.

@@

  Define Chebyshev polynomials $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]

>>>>

  \section{Rank Two}
  Fix integers $b,c>0$ and assume $bc\ge 4$.
  Let $B=\left[ \begin{array}{cc} 0 & -b \\ c & 0 \end{array} \right]$.
  Here we may take $\TT_2$ to have vertices labelled $t_\ell$ for $\ell\in\ZZ$, with $t_{2r}$ joined to $t_{2r+1}$ by an edge labelled $1$ and $t_{2r-1}$ joined to $t_{2r}$ by an edge labelled $2$.
  We aim to understand the dominance regions $\cP(\lambda) = \bigcap_{i\in\ZZ} \phi_{t_i}^{-1} \cC(\phi_{t_i} \lambda)$ for $\lambda\in\ZZ^2$.

@@

  Define \emph{two-parameter Chebyshev polynomials} $u_{i,\varepsilon}$ for $i\in\ZZ$ and $\varepsilon\in\{\pm\}$ recursively by
  \[u_{0,\varepsilon}=0,\quad u_{1,\varepsilon}=1,\quad u_{i+1,\varepsilon}=\begin{cases} bu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=+$;}\\ cu_{i,-\varepsilon}-u_{i-1,\varepsilon} & \text{if $\varepsilon=-$.} \end{cases}\]
  The standard Chebyshev polynomials (of the second kind) are defined by the recursion $u_{i+1}=ru_i-u_{i-1}$, $u_1=1$, $u_0=0$, which can be computed explicitly as
  \[u_i(r)=\frac{1}{2^i\sqrt{r^2-4}}\left(\big(r+\sqrt{r^2-4}\big)^i-\big(r-\sqrt{r^2-4}\big)^i\right).\]
  By the equalities 
  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{\sqrt{c}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{\sqrt{b}}u_i(\sqrt{bc}) & \text{if $i$ is even and $\varepsilon=-$;}\\ u_i(\sqrt{bc}) & \text{if $i$ is odd;} \end{cases}\]
  it follows that $u_{i,\varepsilon}$ can be computed explicitly as
  \[u_{i,\varepsilon}=\begin{cases} \frac{\sqrt{b}}{2^i\sqrt{c(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=+$;}\\ \frac{\sqrt{c}}{2^i\sqrt{b(bc-4)}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is even and $\varepsilon=-$;}\\ \frac{1}{2^i\sqrt{bc-4}}\left(\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i\right) & \text{if $i$ is odd.} \end{cases}\]

  \begin{lemma}
    We have
    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}}=\frac{-bc-\sqrt{bc(bc-4)}}{2b} \qquad \lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}}=\frac{-bc+\sqrt{bc(bc-4)}}{2b}.\]
  \end{lemma}
  \begin{proof}
    For any $i\ge 1$, we have
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}=\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}}.\]
    It follows that
    \[\lim_{i\to\infty} \frac{-u_{i,-}}{u_{i-1,+}} = \lim_{i\to\infty} \left( \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\frac{\sqrt{bc}+\sqrt{bc-4}}{1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}+\sqrt{bc-4}\big),\]
    which is equivalent to the desired expression.
    Similarly, 
    \[\frac{\big(\sqrt{bc}+\sqrt{bc-4}\big)^{i-1}-\big(\sqrt{bc}-\sqrt{bc-4}\big)^{i-1}}{\big(\sqrt{bc}+\sqrt{bc-4}\big)^i-\big(\sqrt{bc}-\sqrt{bc-4}\big)^i}=\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^i\right)},\]
    so that
    \[\lim_{i\to\infty} \frac{-u_{i-1,-}}{u_{i,+}} = \lim_{i\to\infty} \left( \frac{-2\sqrt{c}}{\sqrt{b}}\cdot\frac{\sqrt{bc}-\sqrt{bc-4}}{4\left(1-\left(\frac{\sqrt{bc}-\sqrt{bc-4}}{\sqrt{bc}+\sqrt{bc-4}}\right)^{i-1}\right)} \right) = \frac{-\sqrt{c}}{2\sqrt{b}}\cdot\big(\sqrt{bc}-\sqrt{bc-4}\big),\]
    which is again equivalent to the desired expression.
  \end{proof}
